\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-13 09-30-2014]

### 2014-10-02 paper.tex
merge jeff and zoe
New intro

\begin{abstract}
Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.  Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. Given a GPIS model this would mean sampling from the signed distance field in a uniform grid of side length $n$.  The computational complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D. We propose an alternative to sampling from shape distributions and demonstrate how this reduces the computational complexity to $O(n^3)$ in both 3D and 2D for evaluation of a single grasp. We furthermore introduce the idea of adaptive sampling in the context of choosing the best grasp given a set of grasps and a GPIS object model by formulating it as a budgeted multi-arm bandit problem. We show an order of magnitude reduction in the number of samples needed vs. a non-adaptive approach and we have statistical guarantees with our method. 
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}
Consider a robot packing boxes in a shipping warehouse environment. The robot will frequently encounter objects that it has not seen before. The robot will have to plan stable grasps without any prior information other than its sensor data. As seen in Fig. \ref{fig:noisy data}, with today's RGB and depth sensors, surface properties, such as specularity and transparency, can greatly effect the returned observations. Grasp planners based on deterministic algorithms are not designed to handle such noise and could fail. To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.

A common method to evaluate a grasp with uncertainty is to perform Monte-Carlo integration on a grasp evaluation method. Methods to evaluate a grasp can either be a physics based algorithm \cite{ferrari1992}\cite{pokorny2013classical} or actually trying the grasp in simulation \cite{miller2004graspit} \cite{73}. Since, Monte-Carlo integration requires many evaluations to reach convergences this can be a very computationally intensive operation, when dealing with the problem of choosing the best grasp to select. We show that by framing this problem as a multi-arm bandit problem \cite{barto1998reinforcement}, we can intelligently select which grasps to sample from and  have shown empirically to find the best grasp an order of magnitude faster than a simple uniform sampling policy using only the simplest methods from this field.

@@

We apply our multi-arm bandit approach to an emerging new representation in shape uncertainty, the Gaussian Process Implicit Surface, which puts a Gaussian prior on signed distance fields.  The signed distance fields (SDFs), is a continuous valued function that is an implicit surface: zero-valued at the surface of the object, positive value outside the surface and negative valued inside the surface. This representation is growing in popularity in the robotics field for its ability to integrate range data in real time \cite{newcombe2011kinectfusion}, \cite{curless1996volumetric}. To incorporate uncertainty one can use a Gaussian Process Implicit Surface (GPIS), a Gaussian process over signed distance field. Not only does GPIS present a straightforward and formal way to incorporate measurements from visual, laser and tactile sensors, they  also allow for a continuous differentiable function on shape, which can be used for a feedback grasp controller, finding locally optimal grasps and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.

Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.  A common technique is to sample from the distribution on shape and calculate the quality of grasp on that shape\cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory. In light of this our contributions are the following:

\begin{enumerate}
\item Framing the selection of a grasp as from a given set as a mutli-arm bandit problem 
	\item Derivation of  distributions on grasp parameters given GPIS shape uncertainty model and approach trajectory of gripper.
	\item  Demonstrating both theoretically and empirically how those distributions reduce the computational complexity of sampling.

\end{enumerate}

>>>>

\begin{abstract}
% Gaussian Process Implicit Surface (GPIS) have emerged recently as a new probabilistic shape representation.  Former methods for grasp evaluation with shape uncertainty require sampling from  distributions on shape. Given a GPIS model this would mean sampling from the signed distance field in a uniform grid of side length $n$.  The computational complexity of this operation is $O(n^6)$ in 2D and $O(n^9)$ in 3D. We propose an alternative to sampling from shape distributions and demonstrate how this reduces the computational complexity to $O(n^3)$ in both 3D and 2D for evaluation of a single grasp. We furthermore introduce the idea of adaptive sampling in the context of choosing the best grasp given a set of grasps and a GPIS object model by formulating it as a budgeted multi-arm bandit problem. We show an order of magnitude reduction in the number of samples needed vs. a non-adaptive approach and we have statistical guarantees with our method. 
%Grasp quality evaluation under uncertainty is ...
In new robotic environments, uncertainty in pose and shape can arise from sensor noise, occlusions, and surface properties such as transparency and specularity.
We show that framing grasp quality evaluation as a multi-armed bandit problem provides a principled way to reason about evaluating multiple grasps on an uncertain shape quickly.
We demonstrate this method for planning grasps in the presence of shape uncertainty encoded by a Gaussian process implicit surface (GPIS).
We utilize successive elimination to solve a multi-armed bandit problem and show a speedup in sample complexity versus evaluating grasps using Monte-Carlo integration, a popular method.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

\todo{Get High res GPIS visualizations, Incorporate next round of feedback}

Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
The robot may need to plan grasps for these objects without prior knowledge of their shape and pose.
However, the robot may not be able to measure these quantities exactly due to sensor noise and missing data due to partial visibility and object properties such as transparency.
Grasp planners that assume an exact measurement of shape and pose may fail, for example wh
This motivates using a representation of shape uncertainty to select grasps, but most current methods for evaluating quality under these representations use a brute-force sampling of shapes to evaluate grasp quality, which can be slow.

%To plan grasps in a partially observed world, recent research has focused on incorporating uncertainty in the shape of the object \cite{kehoe2012estimating}, \cite{christopoulos2007handling}, \cite{zheng2005}.
Often when evaluating grasps in this manner, there are a number of grasps that can be quickly shown to be inferior.
When allocating resources to determine the best grasp, this information should be used in order to spend less time evaluating bad grasps.
Multi-armed bandits provide a principled way to reason about evaluating multiple grasps and discarding grasps that are likely to be inferior.

@@

We apply our multi-arm bandit approach to the Gaussian process implicit surface (GPIS), an emerging representation for shapes that gives a formal way to incorporate uncertain measurements from multiple sensors.
GPIS has been recently used in a number of robotic applications, such as a feedback grasp controller, finding locally optimal grasps, and active exploration  \cite{dragiev2011}, \cite{jeffs}, \cite{hollinger2013}.

%Given a method to represent shape uncertainty a policy for grasp sampling, we still need to draw samples from a distribution to evaulate a grasp.  A common technique is to sample from the distribution on shape and calculate the quality of grasp on that shape\cite{kehoe2012estimating}, \cite{kehoe2012toward}, \cite{christopoulos2007handling}. Applying this technique to GPIS requires an exhaustive sampling of the signed distance field, which scales $O(n^6)$ for a 2D $n \times n$ workspace and $O(n^9)$ for a 3D workspace.The computationally complexity of sampling is derived from the fact sampling from a Gaussian requires matrix inversion of the entire signed distance field. Our paper reduces this complexity to $O(n^3)$ by using the insight that for grasp quality evaluation one only cares about the parameters that define a grasp: contacts points, surface normals, center of mass and friction coefficient \cite{pokorny2013classical}. We constrain the contact points by considering the approach trajectory of a gripper.  Hence, sampling the whole signed distance field is not needed, but instead one can only work with the distributions on grasp parameters given the shape uncertainty model and gripper trajectory.

Our contributions are the following:

\begin{enumerate}
	\item Framing the selection of a grasp as from a given set as a multi-arm bandit problem.
	\item Demonstrating empirically that successive elimination, a multi-armed bandit algorithm, reduces the sampling complexity to find a grasp with high expected Ferrari-Canny quality from a set of candidate grasps.	
\end{enumerate}
